Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-04-19 paper/ijcai16.tex
paper: acks in page 7 are fine, keep the last change.

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces.\footnote{Note that max-margin learning has been proposed before \cite{gajos2005} for preference elicitation, 
but with  rudimental methods for query selection.}
Our approach relies on an
extension of max-margin learning to sets, and is effective in the
generation of a diverse set of configurations that can be used to ask
informative preference queries.  The main advantages of this
elicitation method are 1) ability to provide recommendations in large
configuration problems 2) robustness with respect to erroneous
feedback and 3) ability to encourage sparse utility functions.
Experimental comparisons against state-of-the-art Bayesian preference
elicitation strategies confirm these advantages. Future work includes
extending the approach to truly hybrid scenarios (where real valued
attributes do not depend on categorical ones) and studying its
applicability to other problems, \paolo{as the identification of Choquet models \cite{Pine2013}}.

>>>>

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces.\footnote{Note that max-margin learning has been proposed before \cite{gajos2005} for preference elicitation, 
but with  rudimental methods for query selection.}
Our approach relies on an
extension of max-margin learning to sets, and is effective in the
generation of a diverse set of configurations that can be used to ask
informative preference queries.  The main advantages of this
elicitation method are 1) ability to provide recommendations in large
configuration problems 2) robustness with respect to erroneous
feedback and 3) ability to encourage sparse utility functions.
Experimental comparisons against state-of-the-art Bayesian preference
elicitation strategies confirm these advantages. Future work includes
extending the approach to truly hybrid scenarios (where real valued
attributes do not depend on categorical ones) and studying its
applicability to other problems, as the identification of Choquet models
\cite{Pine2013}.
